Why is it that statistical tests for residuals are not widely used? An explanation using visual inference.

### 2023-01-10 paper_comparison/paper_comparison/paper_comparison.Rmd
update caption of example lineups

Figure \ref{fig:polypower} shows the estimated power of visual test on lineups produced by the non-linearity model with $X_{raw} \sim U(-1,1)$, against the natural logarithm of the effect $log_e(E)$, with a 5% significance level. Lineups with $X_{raw} \sim U(-1,1)$ are focused in this section because visual patterns are more likely to be revealed under the uniform distribution. Besides, we have collected more responses for this distribution in experiment III to produce more reliable and stable power curves. Power analysis of other distributions can be found in Section [?]. At the bottom of the figure \ref{fig:polypower}, there are a sequence of example residual plots with increasing levels of $log_e(E)$. Readers can evaluate them from left to right and determine at which level the departure from a good residual plot becomes detectable.

@@

Overall, the power comparison suggests that conventional tests differs significantly from visual tests in these two scenarios. Visual test have much higher tolerance of the residual departures than the conventional test. Since fail to reject $H_0$ in a visual test usually means that there are no obvious visual discoveries found in the residual plot, analysts and the general public as the consumers of the output may not be convinced of the existence of significant residual departures in spite of the rejection of $H_0$ given by the conventional test. Even if the rejection is accepted, the model violation may be considered as impactless due to the fact that they are not clearly visible. Besides, the sensitivity of the conventional test could also distract and discourage analysts from finding simple but good linear approximation to the data. The rejection of $H_0$ because of human acceptable and negligible residual departures is not practically meaningful and useful. This may limit the popularity of conventional tests in residual diagnostics among analysts.

@@

The power comparison illustrates that appropriate conventional tests reject $H_0$ more often than visual tests. In this section, we explore how often they agree with each other by investigate the rejection rates based on $p$-values.

@@

For easy lineups produced by the non-linearity model, 65% are rejected by both the conventional and visual tests, while 9% are accepted by both tests. Thus, 74% of the time two tests will agree with each other. There are 16% of lineups rejected by the conventional test only.

Interestingly, in spite of the greater power of the conventional test, 10% of the lineups are rejected by the visual test only. Recall that the RESET test used in our analysis includes powers of fitted values up to four. However, the "M" and the "Triple-U" shapes constructed from the Hermite polynomials contain powers of the regressor up to six and 18 respectively. In fact, by including the powers of fitted values up to six in the RESET test, all cases will be rejected. We also can observe from the example plot displayed in Figure \ref{fig:easy-poly-example} that panel three is distinctly different from others, exhibiting a "M" shape. This clearly suggests users of the RESET test and any other residual-based conventional tests that require the specification of variables of interest to check the residual plot before conducting the test, such that the correct choice of variables can be made.

```{r easy-poly-example, fig.height = 5, fig.cap = "Lineup poly-270 produced by the non-linearity model used in experiment I and III. It is rejected by the visual test but not by the RESET test. The data plot at panel three exhibits strong non-linear pattern."}
VI_MODEL$plot_lineup(vi_lineup$poly_270$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

@@

```{r easy-heter-example1, fig.height = 5, fig.cap = 'Lineup heter-331 produced by the heteroskedasticity model used in experiment II and III. It is rejected by the visual test but not by the  Breusch-Pagan test. The data plot at panel 17 contains a "Butterfly" shape, indicating the presence of heteroskedasticity.'}
VI_MODEL$plot_lineup(vi_lineup$heter_331$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

```{r easy-heter-example2, fig.height = 5, fig.cap = "Lineup heter-536 produced by the heteroskedasticity model used in experiment II. It is rejected by the visual test but not by the  Breusch-Pagan test. The data plot at panel 18 exhibits a vague heteroskedasticity pattern, but it contains a distinct outlier which makes it attractive to subjects."}
VI_MODEL$plot_lineup(vi_lineup$heter_536$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

@@

```{r moderate-heter-example1, fig.height = 5, fig.cap = "Lineup heter-219 produced by the heteroskedasticity model used in experiment II. It is rejected by the visual test but not by the  Breusch-Pagan test. Though the data plot at panel 14 shows no heteroskedasticity patterns, it contains a few outliers at the bottom of the panel."}
VI_MODEL$plot_lineup(vi_lineup$heter_219$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

@@

```{r difficult-heter-example1, fig.height = 5, fig.cap = "Lineup heter-224 produced by the heteroskedasticity model used in experiment II. It is rejected by the visual test but not by the  Breusch-Pagan test. Although two out of five subjects correctly identify the data plot at panel 5, it does not exhibit any visually distinguishable pattern."}
VI_MODEL$plot_lineup(vi_lineup$heter_224$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

```{r difficult-heter-example2, fig.height = 5, fig.cap = "Lineup heter-415 produced by the heteroskedasticity model used in experiment II. It is rejected by the visual test but not by the  Breusch-Pagan test. Panel 15 is the data plot but it does not exhibit any visually distinguishable pattern."}
VI_MODEL$plot_lineup(vi_lineup$heter_415$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

@@

## Effect of the distribution of the independent variable

# change of x_dist -> power

# appendix (contains all the details)

@@

### A collection interesting lineups (unusual results)

>>>>

Figure \ref{fig:polypower} shows the estimated power of visual test on lineups produced by the non-linearity model with $X_{raw} \sim U(-1,1)$, against the natural logarithm of the effect $log_e(E)$, with a 5% significance level. Uniform distribution is the focus of this section because visual patterns are more likely to be revealed. Besides, six more evaluations are collected for the uniform distribution in experiment III, which will produce more reliable and stable power curves. Analysis of other distributions can be found in Section \ref{effect-of-the-distribution-of-the-regressor}. At the bottom of the figure \ref{fig:polypower}, there are a sequence of example residual plots with increasing levels of $log_e(E)$. Readers can evaluate them from left to right and determine at which level the departure from a good residual plot becomes detectable.

@@

Overall, the power comparison suggests that conventional tests differs significantly from visual tests in two regression diagnostics scenarios designed by us. Visual test have much higher tolerance of the residual departures than the conventional test. Since fail to reject $H_0$ in a visual test usually means that there are no obvious visual discoveries found in the residual plot, analysts and the general public as the consumers of the output may not be convinced of the existence of significant residual departures in spite of the rejection of $H_0$ given by the conventional test. Even if the rejection is accepted, the model violation may be considered as impactless due to the fact that they are not clearly visible. Besides, the sensitivity of the conventional test could also distract and discourage analysts from finding simple but good linear approximation to the data. The rejection of $H_0$ because of human acceptable and negligible residual departures is not practically meaningful and useful. This may limit the popularity of conventional tests in residual diagnostics among analysts.

@@

The power comparison illustrates that appropriate conventional tests reject $H_0$ more aggressively than visual tests. In this section, we explore how often they agree with each other by investigate the rejection rates based on $p$-values.

@@

For easy lineups produced by the non-linearity model, 65% are rejected by both the conventional and visual tests, while 9% are accepted by both tests. Thus, 74% of the time two tests will agree with each other. There are 16% of lineups rejected by conventional tests only.

Interestingly, in spite of the greater power of conventional tests, 10% of the lineups are rejected by visual tests only. Recall that the RESET test used in our analysis includes powers of fitted values up to four. However, the "M" and the "Triple-U" shapes constructed from the Hermite polynomials contain power of the regressor up to six and 18 respectively. In fact, by including the power of fitted values up to six in the RESET test, all these cases will be rejected. We also can observe from the example plot displayed in Figure \ref{fig:easy-poly-example} that panel three is distinctly different from others, exhibiting a "M" shape. This clearly suggests users of the RESET test and any other residual-based conventional tests that require the specification of variables of interest to check the residual plot before conducting the test, such that the correct choice of variables can be made.

```{r easy-poly-example, fig.height = 5, fig.cap = "Lineup poly-270 with $log_e(E) = 3.89$ produced by the non-linearity model used in experiment I and III. It is rejected by the visual test but not by the RESET test. The data plot at panel three exhibits strong non-linear pattern."}
VI_MODEL$plot_lineup(vi_lineup$poly_270$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

@@

```{r easy-heter-example1, fig.height = 5, fig.cap = 'Lineup heter-331 with $log_e(E) = 4.02$ produced by the heteroskedasticity model used in experiment II and III. It is rejected by the visual test but not by the  Breusch-Pagan test. The data plot at panel 17 contains a "Butterfly" shape, indicating the presence of heteroskedasticity.'}
VI_MODEL$plot_lineup(vi_lineup$heter_331$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

```{r easy-heter-example2, fig.height = 5, fig.cap = "Lineup heter-536 with $log_e(E) = 4.13$ produced by the heteroskedasticity model used in experiment II. It is rejected by the visual test but not by the  Breusch-Pagan test. The data plot at panel 18 exhibits a vague heteroskedasticity pattern, but it contains a distinct outlier which makes it attractive to subjects."}
VI_MODEL$plot_lineup(vi_lineup$heter_536$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

@@

```{r moderate-heter-example1, fig.height = 5, fig.cap = "Lineup heter-219 with $log_e(E) = 1.61$ produced by the heteroskedasticity model used in experiment II. It is rejected by the visual test but not by the  Breusch-Pagan test. Though the data plot at panel 14 shows no heteroskedasticity patterns, it contains a few outliers at the bottom of the panel."}
VI_MODEL$plot_lineup(vi_lineup$heter_219$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

@@

```{r difficult-heter-example1, fig.height = 5, fig.cap = "Lineup heter-224 with $log_e(E) = 1.32$ produced by the heteroskedasticity model used in experiment II. It is rejected by the visual test but not by the  Breusch-Pagan test. Although two out of five subjects correctly identify the data plot at panel 5, it does not exhibit any visually distinguishable pattern."}
VI_MODEL$plot_lineup(vi_lineup$heter_224$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

```{r difficult-heter-example2, fig.height = 5, fig.cap = "Lineup heter-415 with $log_e(E) = -0.31$ produced by the heteroskedasticity model used in experiment II. It is rejected by the visual test but not by the  Breusch-Pagan test. Panel 15 is the data plot but it does not exhibit any visually distinguishable pattern."}
VI_MODEL$plot_lineup(vi_lineup$heter_415$data, 
                     remove_grid_line = TRUE, 
                     theme = theme_light(),
                     remove_axis = TRUE)
```

@@

## Effect of the distribution of the regressor

```{r fig.height = 3, fig.width = 5}
vi_survey %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "polynomial") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(x_dist = ifelse(x_dist == "even_discrete", 
                         "Discrete", 
                         stringr::str_to_title(x_dist))) %>%
  ggplot() +
  geom_smooth(data = mutate(poly_conv_sim, 
                            log_effect_size = log(effect_size)) %>%
                select(x_dist, log_effect_size, RESET4_p_value) %>%
                rename(RESET_p_value = RESET4_p_value) %>%
                pivot_longer(RESET_p_value) %>%
                mutate(x_dist = ifelse(x_dist == "even_discrete", 
                                       "Discrete", 
                                       stringr::str_to_title(x_dist))) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, 
                  as.numeric(value < 0.05), 
                  col = x_dist,
                  linetype = "RESET"), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  geom_smooth(aes(log_effect_size, 
                  reject, 
                  col = x_dist,
                  linetype = "Visual"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE) +
  theme_light(base_size = 5) +
  scale_color_manual(values = rev(rcartocolor::carto_pal(5, "Vivid"))) +
  scale_size_manual(values = c(1, 2, 3)) +
  scale_linetype_manual(values = c("longdash", "solid")) +
  guides(linetype = guide_legend(nrow = 2), col = guide_legend(nrow = 2)) +
  theme(legend.position = "bottom", legend.key.width = unit(1.5, "cm")) +
  xlab("Effect size (log e)") +
  ylab("Power") +
  labs(col = "Distribution of regressor", linetype = "Test")
```

```{r fig.height = 3, fig.width = 5}
vi_survey %>%
  group_by(unique_lineup_id) %>%
  summarise(across(everything(), first)) %>%
  filter(type == "heteroskedasticity") %>%
  filter(!null_lineup) %>%
  filter(!attention_check) %>%
  mutate(reject = as.numeric(p_value <= 0.05)) %>%
  mutate(log_effect_size = log(effect_size)) %>%
  mutate(x_dist = ifelse(x_dist == "even_discrete", 
                         "Discrete", 
                         stringr::str_to_title(x_dist))) %>%
  ggplot() +
  geom_smooth(data = mutate(heter_conv_sim, 
                            log_effect_size = log(effect_size)) %>%
                select(x_dist, log_effect_size, BP_p_value) %>%
                pivot_longer(BP_p_value) %>%
                mutate(x_dist = ifelse(x_dist == "even_discrete", 
                                       "Discrete", 
                                       stringr::str_to_title(x_dist))) %>%
                mutate(name = gsub("_p_value", " test", name)), 
              aes(log_effect_size, 
                  as.numeric(value < 0.05), 
                  col = x_dist,
                  linetype = "BP"), 
              method = "glm", 
              method.args = list(family = binomial),
              se = FALSE) +
  geom_smooth(aes(log_effect_size, 
                  reject, 
                  col = x_dist,
                  linetype = "Visual"), 
              method = "glm", 
              method.args = list(family = binomial), 
              se = FALSE) +
  theme_light(base_size = 5) +
  scale_color_manual(values = rev(rcartocolor::carto_pal(5, "Vivid"))) +
  scale_size_manual(values = c(1, 2, 3)) +
  scale_linetype_manual(values = c("longdash", "solid")) +
  guides(linetype = guide_legend(nrow = 2), col = guide_legend(nrow = 2)) +
  theme(legend.position = "bottom", legend.key.width = unit(1.5, "cm")) +
  xlab("Effect size (log e)") +
  ylab("Power") +
  labs(col = "Distribution of regressor", linetype = "Test")
```

(change of x_dist -> power)

# Appendix

## Effect derivation

## $p$-value scatter plot

@@

## A collection interesting lineups (unusual results)

### 2023-01-10 paper_comparison/paper_comparison/paper_comparison.tex
update caption of example lineups

Figure \ref{fig:polypower} shows the estimated power of visual test on
lineups produced by the non-linearity model with
\(X_{raw} \sim U(-1,1)\), against the natural logarithm of the effect
\(log_e(E)\), with a 5\% significance level. Lineups with
\(X_{raw} \sim U(-1,1)\) are focused in this section because visual
patterns are more likely to be revealed under the uniform distribution.
Besides, we have collected more responses for this distribution in
experiment III to produce more reliable and stable power curves. Power
analysis of other distributions can be found in Section {[}?{]}. At the
bottom of the figure \ref{fig:polypower}, there are a sequence of
example residual plots with increasing levels of \(log_e(E)\). Readers
can evaluate them from left to right and determine at which level the
departure from a good residual plot becomes detectable.

@@

Overall, the power comparison suggests that conventional tests differs
significantly from visual tests in these two scenarios. Visual test have
much higher tolerance of the residual departures than the conventional
test. Since fail to reject \(H_0\) in a visual test usually means that
there are no obvious visual discoveries found in the residual plot,
analysts and the general public as the consumers of the output may not
be convinced of the existence of significant residual departures in
spite of the rejection of \(H_0\) given by the conventional test. Even
if the rejection is accepted, the model violation may be considered as
impactless due to the fact that they are not clearly visible. Besides,
the sensitivity of the conventional test could also distract and
discourage analysts from finding simple but good linear approximation to
the data. The rejection of \(H_0\) because of human acceptable and
negligible residual departures is not practically meaningful and useful.
This may limit the popularity of conventional tests in residual
diagnostics among analysts.

@@

The power comparison illustrates that appropriate conventional tests
reject \(H_0\) more often than visual tests. In this section, we explore
how often they agree with each other by investigate the rejection rates
based on \(p\)-values.

@@

For easy lineups produced by the non-linearity model, 65\% are rejected
by both the conventional and visual tests, while 9\% are accepted by
both tests. Thus, 74\% of the time two tests will agree with each other.
There are 16\% of lineups rejected by the conventional test only.

Interestingly, in spite of the greater power of the conventional test,
10\% of the lineups are rejected by the visual test only. Recall that
the RESET test used in our analysis includes powers of fitted values up
to four. However, the ``M'' and the ``Triple-U'' shapes constructed from
the Hermite polynomials contain powers of the regressor up to six and 18
respectively. In fact, by including the powers of fitted values up to
six in the RESET test, all cases will be rejected. We also can observe
from the example plot displayed in Figure \ref{fig:easy-poly-example}
that panel three is distinctly different from others, exhibiting a ``M''
shape. This clearly suggests users of the RESET test and any other
residual-based conventional tests that require the specification of
variables of interest to check the residual plot before conducting the
test, such that the correct choice of variables can be made.

@@

\caption{Lineup poly-270 produced by the non-linearity model used in experiment I and III. It is rejected by the visual test but not by the RESET test. The data plot at panel three exhibits strong non-linear pattern.}\label{fig:easy-poly-example}
\end{figure}

@@

\caption{Lineup heter-331 produced by the heteroskedasticity model used in experiment II and III. It is rejected by the visual test but not by the  Breusch-Pagan test. The data plot at panel 17 contains a "Butterfly" shape, indicating the presence of heteroskedasticity.}\label{fig:easy-heter-example1}
\end{figure}

@@

\caption{Lineup heter-536 produced by the heteroskedasticity model used in experiment II. It is rejected by the visual test but not by the  Breusch-Pagan test. The data plot at panel 18 exhibits a vague heteroskedasticity pattern, but it contains a distinct outlier which makes it attractive to subjects.}\label{fig:easy-heter-example2}
\end{figure}

@@

\caption{Lineup heter-219 produced by the heteroskedasticity model used in experiment II. It is rejected by the visual test but not by the  Breusch-Pagan test. Though the data plot at panel 14 shows no heteroskedasticity patterns, it contains a few outliers at the bottom of the panel.}\label{fig:moderate-heter-example1}
\end{figure}

@@

\caption{Lineup heter-224 produced by the heteroskedasticity model used in experiment II. It is rejected by the visual test but not by the  Breusch-Pagan test. Although two out of five subjects correctly identify the data plot at panel 5, it does not exhibit any visually distinguishable pattern.}\label{fig:difficult-heter-example1}
\end{figure}

@@

\caption{Lineup heter-415 produced by the heteroskedasticity model used in experiment II. It is rejected by the visual test but not by the  Breusch-Pagan test. Panel 15 is the data plot but it does not exhibit any visually distinguishable pattern.}\label{fig:difficult-heter-example2}
\end{figure}

@@

\hypertarget{effect-of-the-distribution-of-the-independent-variable}{%
\subsection{Effect of the distribution of the independent
variable}\label{effect-of-the-distribution-of-the-independent-variable}}

\hypertarget{change-of-x_dist---power}{%
\section{change of x\_dist -\textgreater{}
power}\label{change-of-x_dist---power}}

\hypertarget{appendix-contains-all-the-details}{%
\section{appendix (contains all the
details)}\label{appendix-contains-all-the-details}}

\hypertarget{a-collection-interesting-lineups-unusual-results}{%
\subsubsection{A collection interesting lineups (unusual
results)}\label{a-collection-interesting-lineups-unusual-results}}

>>>>

Figure \ref{fig:polypower} shows the estimated power of visual test on
lineups produced by the non-linearity model with
\(X_{raw} \sim U(-1,1)\), against the natural logarithm of the effect
\(log_e(E)\), with a 5\% significance level. Uniform distribution is the
focus of this section because visual patterns are more likely to be
revealed. Besides, six more evaluations are collected for the uniform
distribution in experiment III, which will produce more reliable and
stable power curves. Analysis of other distributions can be found in
Section \ref{effect-of-the-distribution-of-the-regressor}. At the bottom
of the figure \ref{fig:polypower}, there are a sequence of example
residual plots with increasing levels of \(log_e(E)\). Readers can
evaluate them from left to right and determine at which level the
departure from a good residual plot becomes detectable.

@@

Overall, the power comparison suggests that conventional tests differs
significantly from visual tests in two regression diagnostics scenarios
designed by us. Visual test have much higher tolerance of the residual
departures than the conventional test. Since fail to reject \(H_0\) in a
visual test usually means that there are no obvious visual discoveries
found in the residual plot, analysts and the general public as the
consumers of the output may not be convinced of the existence of
significant residual departures in spite of the rejection of \(H_0\)
given by the conventional test. Even if the rejection is accepted, the
model violation may be considered as impactless due to the fact that
they are not clearly visible. Besides, the sensitivity of the
conventional test could also distract and discourage analysts from
finding simple but good linear approximation to the data. The rejection
of \(H_0\) because of human acceptable and negligible residual
departures is not practically meaningful and useful. This may limit the
popularity of conventional tests in residual diagnostics among analysts.

@@

The power comparison illustrates that appropriate conventional tests
reject \(H_0\) more aggressively than visual tests. In this section, we
explore how often they agree with each other by investigate the
rejection rates based on \(p\)-values.

@@

For easy lineups produced by the non-linearity model, 65\% are rejected
by both the conventional and visual tests, while 9\% are accepted by
both tests. Thus, 74\% of the time two tests will agree with each other.
There are 16\% of lineups rejected by conventional tests only.

Interestingly, in spite of the greater power of conventional tests, 10\%
of the lineups are rejected by visual tests only. Recall that the RESET
test used in our analysis includes powers of fitted values up to four.
However, the ``M'' and the ``Triple-U'' shapes constructed from the
Hermite polynomials contain power of the regressor up to six and 18
respectively. In fact, by including the power of fitted values up to six
in the RESET test, all these cases will be rejected. We also can observe
from the example plot displayed in Figure \ref{fig:easy-poly-example}
that panel three is distinctly different from others, exhibiting a ``M''
shape. This clearly suggests users of the RESET test and any other
residual-based conventional tests that require the specification of
variables of interest to check the residual plot before conducting the
test, such that the correct choice of variables can be made.

@@

\caption{Lineup poly-270 with $log_e(E) = 3.89$ produced by the non-linearity model used in experiment I and III. It is rejected by the visual test but not by the RESET test. The data plot at panel three exhibits strong non-linear pattern.}\label{fig:easy-poly-example}
\end{figure}

@@

\caption{Lineup heter-331 with $log_e(E) = 4.02$ produced by the heteroskedasticity model used in experiment II and III. It is rejected by the visual test but not by the  Breusch-Pagan test. The data plot at panel 17 contains a "Butterfly" shape, indicating the presence of heteroskedasticity.}\label{fig:easy-heter-example1}
\end{figure}

@@

\caption{Lineup heter-536 with $log_e(E) = 4.13$ produced by the heteroskedasticity model used in experiment II. It is rejected by the visual test but not by the  Breusch-Pagan test. The data plot at panel 18 exhibits a vague heteroskedasticity pattern, but it contains a distinct outlier which makes it attractive to subjects.}\label{fig:easy-heter-example2}
\end{figure}

@@

\caption{Lineup heter-219 with $log_e(E) = 1.61$ produced by the heteroskedasticity model used in experiment II. It is rejected by the visual test but not by the  Breusch-Pagan test. Though the data plot at panel 14 shows no heteroskedasticity patterns, it contains a few outliers at the bottom of the panel.}\label{fig:moderate-heter-example1}
\end{figure}

@@

\caption{Lineup heter-224 with $log_e(E) = 1.32$ produced by the heteroskedasticity model used in experiment II. It is rejected by the visual test but not by the  Breusch-Pagan test. Although two out of five subjects correctly identify the data plot at panel 5, it does not exhibit any visually distinguishable pattern.}\label{fig:difficult-heter-example1}
\end{figure}

@@

\caption{Lineup heter-415 with $log_e(E) = -0.31$ produced by the heteroskedasticity model used in experiment II. It is rejected by the visual test but not by the  Breusch-Pagan test. Panel 15 is the data plot but it does not exhibit any visually distinguishable pattern.}\label{fig:difficult-heter-example2}
\end{figure}

@@

\hypertarget{effect-of-the-distribution-of-the-regressor}{%
\subsection{Effect of the distribution of the
regressor}\label{effect-of-the-distribution-of-the-regressor}}

\begin{center}\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-14-1} \end{center}

\begin{center}\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-15-1} \end{center}

(change of x\_dist -\textgreater{} power)

\hypertarget{appendix}{%
\section{Appendix}\label{appendix}}

\hypertarget{effect-derivation}{%
\subsection{Effect derivation}\label{effect-derivation}}

\hypertarget{p-value-scatter-plot}{%
\subsection{\texorpdfstring{\(p\)-value scatter
plot}{p-value scatter plot}}\label{p-value-scatter-plot}}

\hypertarget{a-collection-interesting-lineups-unusual-results}{%
\subsection{A collection interesting lineups (unusual
results)}\label{a-collection-interesting-lineups-unusual-results}}
